Characteristic polynomials of p-adic matrices

### 2017-02-03 charpoly/charpoly.tex
Minor improvements.

\begin{prop} 
Algorithm 1 computes $H$ and $P$ realizing an approximate Hessenberg form of $M.$
$P$ is exact over finite extensions of $\mathbb{Q}_p$ and $k((X))$, and the computation is in $O(n^3)$ operations in $K$ at precision the maximum precision of a coefficent in $M.$
\end{prop}
\begin{proof}
Let us assume that $K$ is a finite extensions of $\mathbb{Q}_p$ or $k((X)).$
Inside the nested \textbf{for} loop, if we want to eliminate $p^{u_y} \varepsilon_y+O(p^{n_y})$ with pivot $p^{u_x} \varepsilon_x+O(p^{n_x}),$
with the $\varepsilon$'s being units,
the corresponding coefficient of the corresponding shear matrix is the lift (in $\mathbb{Z}, $  $k[X]$ or adequate extension) of $p^{u_y-u_x} \varepsilon_y \varepsilon_x^{-1} \mod \pi^{\min (n_x,n_y)}.$
Exactness follows directly. Over other fields, we can not lift, but the computations are still valid.
The rest is clear.
\end{proof}

@@

Now, instead of computing directly $Q$, we first compute a matrix $R$ 
with the property that $N^t = R N R^{-1}$. For that, we apply the same
strategy as above except that we start with the vector $e = (1, 0, 
\ldots, 0)$ (and not with a random vector). A simple computation shows
that, for $1 \leq i \leq n{-}1$, the vector $N^i e$ has the shape:
$$N^i e = (0, \ldots, 0, -a_0, \star, \ldots, \star)$$
with $n{-}i$ starting zeros. Therefore the $N^i e$'s form a basis of
$K^n$, \emph{i.e.} $e$ is always a cyclic vector of $N$. Once $R$ has
been compute, we recover $Q$ using the relation $Q = P_\inv^t R$.

>>>>

\begin{prop} 
Algorithm 1 computes $H$ and $P$ realizing an approximate Hessenberg form of $M.$
$P$ is exact over finite extensions of $\mathbb{Q}_p$ and $k((X))$, and the computation is in $O(n^3)$ operations in $K$ at precision the maximum precision of a coefficent in $M.$
\end{prop}
\begin{proof}
Let us assume that $K$ is a finite extensions of $\mathbb{Q}_p$ or $k((X)).$
Inside the nested \textbf{for} loop, if we want to eliminate $p^{u_y} \varepsilon_y+O(p^{n_y})$ with pivot $p^{u_x} \varepsilon_x+O(p^{n_x}),$
with the $\varepsilon$'s being units,
the corresponding coefficient of the corresponding shear matrix is the lift(in $\mathbb{Z}, $  $\mathbb{F}_q[X],$ $\mathbb{Q}[X]$ or adequate extension) of $p^{u_y-u_x} \varepsilon_y \varepsilon_x^{-1} \mod \pi^{\min (n_x,n_y)}.$
Exactness follows directly. Over other fields, we can not lift, but the computations are still valid.
The rest is clear.
\end{proof}

@@

Now, instead of computing directly $Q$, we first compute a matrix $R$ 
with the property that $N^t = R N R^{-1}$. For that, we apply the same
strategy as above except that we start with the vector $e = (1, 0, 
\ldots, 0)$ (and not with a random vector). A simple computation shows
that, for $1 \leq i \leq n{-}1$, the vector $N^i e$ has the shape:
$$N^i e = (0, \ldots, 0, -a_0, \star, \ldots, \star)$$
with $n{-}i$ starting zeros. Therefore the $N^i e$'s form a basis of
$K^n$, \emph{i.e.} $e$ is always a cyclic vector of $N$. Once $R$ has
been computed, we recover $Q$ using the relation $Q = P_\inv^t R$.
